\textls[-0]{\thetitle}

### 2023-03-17 metatheory-condensed.tex
edit

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
\mathit{self}_i : A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
For readability, we use a notation with explicit names
in this typing judgment:
we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
and write its type~$A_i$, which is a dependent tuple type, as a
dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

>>>>

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
\mathit{self}_i : A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
The context types $A_i$ are a dependent tuple type, but for readability,
we write them as dependent record types that give labels to the fields.
%we use a notation with explicit names
%in this typing judgment:
%we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
%and write its type~$A_i$, which is a dependent tuple type, as a
%dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]
